%!TEX root = main.tex

\section{Evaluation}\label{sec:eval}

%In this section, we briefly analyse and compare our 2FA protocol with the smart-card-based protocol proposed in  \cite{WangW18} and the hardware token-based protocol in \cite{JareckiJKSS21} as the latter two protocols are relatively efficient, do not use secure chipsets, and they consider the same security threats as we do. We summarise the analysis result in Table \ref{comparisonTable}. We refer readers to \prettyref{app:long-eval} for a more detailed evaluation. 



In this section, we briefly analyse and compare the 2FA protocol we presented in Section \ref{sec::the-protocol} with the smart-card-based protocol proposed in  \cite{WangW18}, the hardware token-based protocol in \cite{JareckiJKSS21}, and the symmetric-key-based scheme in  \cite{MatsuoMY11}.  We consider the protocols in  \cite{WangW18,JareckiJKSS21} because they are relatively efficient, do not rely on secure hardware, and consider the same security threats as we do, \ie., resistance against card/token loss, against an offline attack, and against a corrupt server. We also include the scheme in  \cite{MatsuoMY11}  in our analysis because it is highly efficient, only uses symmetric-key primitives, and is in the standard model. Table \ref{comparisonTable} summarises the analysis result. We refer readers to \prettyref{app:long-eval} for a more detailed evaluation. 


%Before we compare the two protocols' costs, we highlight a vital difference between the two. 

\input{evaluation-table}

\subsection{Computation Cost}
In our protocol, each party (user or server) invokes the authenticated encryption scheme $4$ times and the pseudorandom function $5$ times. In the protocol proposed by Wang \etal~\cite{WangW18}, the user invokes a hash function $11$ times and performs $3$ modular exponentiations while the server invokes the hash function $8$ times and performs $2$ modular exponentiations. Moreover, in the protocol presented by Jarecki \etal~\cite{JareckiJKSS21}, the user invokes a hash function $3$ times and runs symmetric key encryption once. It also performs $10$ modular exponentiations. While the server invokes a pseudorandom function once and performs at least $2$ modular exponentiations and $2$ symmetric-key encryptions. 


Now, we focus on the protocol proposed in \cite{MatsuoMY11}. The scheme assumes the user and server have already agreed on the user's password. 
%
In total, the user (and the trusted chipset) invokes the verification algorithm of a Message Authentication Code (MAC) scheme once and the pseudorandom function three times. The server cost is similar to the user's cost, with the difference that the server also invokes the tag generator algorithm of the MAC scheme once. The scheme does not involve any modular exponentiations. 

Thus,  our protocol, along with those in \cite{WangW18,JareckiJKSS21,MatsuoMY11} uses a constant number of symmetric-key primitive invocations. However, our protocol and the protocol in \cite{MatsuoMY11} avoid modular exponentiations, resulting in a lower cost compared to the protocols  \cite{WangW18,JareckiJKSS21}.

When executed on the extremely low-power microcontrollers common in dedicated hardware authentication tokens, \textbf{asymmetric cryptography consumes approximately 1000 times more energy than its corresponding symmetric counterpart}~\cite{energyconsumption}. These tokens are designed to function for several years without battery replacements, typically lacking user-replaceable or rechargeable batteries to cut manufacturing costs and enhance tamper resistance. \textbf{The power saving that results from using solely symmetric primitives is therefore important for feasibility}.
For the commercial product that this protocol was implemented for, there was no available on the market that was both cost-effective and able to execute asymmetric cryptography with a speed that would result in a good user experience.



%Thus,  our protocol and the ones in \cite{WangW18,JareckiJKSS21} involve a constant number of symmetric key primitive invocations; however, our protocol does not involve any modular exponentiations, whereas those in  \cite{WangW18,JareckiJKSS21} involve a constant number of modular exponentiations which leads to a higher cost. 
%The avoidance of the need to perform modular exponentiations not only reduces computation cost and energy consumption but also saves flash storage due to not requiring a big integer library.

\subsection{Communication Cost}

In our protocol, the communication cost of the user is $1268$ bits and the server is $1536$ bits. However, in the protocol proposed in \cite{WangW18},  the communication cost of the user is $1952$ bits and the server is  $1184$ bits; while in the protocol developed in \cite{JareckiJKSS21} the user's and server's communication costs are at least $2856$ and $1044$ bits respectively. Next, we focus on the communication cost of the protocol in \cite{MatsuoMY11}. In total, the user for each authentication sends   $(r_{\sss A}, ID_{\sss A}, Auth_{\sss A})$ to the server. The server also sends $(r_{\sss A}, r_{\sss B}, ID_{\sss B}, Auth_{\sss B})$ to the user, where each message is of size $128$-bit. Thus, the protocol's total communication cost is $896$ bits. 


Hence, our protocol imposes a $10\%$ and $40\%$ lower communication cost than the protocols in \cite{WangW18} and \cite{JareckiJKSS21} that are secure against a corrupted token or server. The protocol in \cite{MatsuoMY11} has the lowest communication cost but it is not secure against a corrupted server. 

When communication is implemented using a 2-D barcode, this reduction in message size as compared to the-state-of-the-art allows for an increased level of error correction in the generated barcodes. Consequently, the decoding process becomes more resilient to inaccurate alignment and issues like reflections on the client screen, therefore improving user experience through a reduction in time needed to capture a valid barcode.



\subsection{Other Features}
 In our protocol, a user needs to know and type into the token only a single secret, \ie, a PIN. Furthermore, we do not put any trust assumptions on users' personal computers (or clients). Therefore, they can be corrupted at any time, e.g., simultaneously when another party such as the token or server is corrupted. 
 
 In contrast, in the protocol in \cite{WangW18}, a user has to know and type an additional secret, \ie, a random ID. As shown by Scott~\cite{Scott12a}, this scheme will not remain secure, even if only the user's ID is revealed. Also, in this scheme, users type in their PINs into another device, i.e., a card reader. For the security of the scheme holds, it is required that the card reader be fully trusted, in the case where the server or smart card is breached. 
 
  
   Similarly, the protocol in \cite{JareckiJKSS21} requires users to insert their PINs into their personal computers instead of inserting them into the dedicated hardware token; this approach is problematic as the PINs will be at a higher risk of being exposed to attackers because users' computers are (i) often connected to the Internet, and (ii) used for various purposes, consequently, they are more likely to be broken into. Furthermore, the protocol relies on an additional trusted party as well, i.e., trusted users' computers. Specifically, for the protocol's security to hold, it is required that users' personal computers are fully trusted, in the case where the token or the server is corrupted, which is not desirable. In contrast, our protocol requires users to insert their PIN into the hardware token that is used only for authentication and is always disconnected from the Internet. 
 
 In the protocol in \cite{MatsuoMY11} a user needs to know only a single PIN. It requires the server to be fully trusted and it uses a trusted chipset. So, it relies on the strongest security assumption. 
 % 
Our protocol and the one in \cite{MatsuoMY11} are secure in the standard model whereas the protocols in \cite{WangW18,JareckiJKSS21} are in the non-standard random oracle model. 




%Hence, our protocol imposes $10\%$ and $40\%$ lower communication costs than the protocols in \cite{WangW18} and \cite{JareckiJKSS21} do respectively.


%\subsection{Other Features}
% In our protocol, a user needs to know and type into the device only a single secret, \ie, a PIN. Furthermore, we do not put any trust assumptions on users' personal computers (or clients). Therefore, they can be corrupted at any time, e.g., simultaneously when another party such as the token or server is corrupted. 
% 
% In contrast, in the protocol in \cite{WangW18}, a user has to know and type an additional secret, \ie, a random ID. As shown by Scott~\cite{Scott12a}, this scheme will not remain secure, even if only the user's ID is revealed. Also, in this scheme, users type in their PINs into another device, i.e., a card reader. For the security of the scheme holds, it is required that the card reader be fully trusted, in the case where the server or smart card is breached. 
% 
%  
%   Similarly, the protocol in \cite{JareckiJKSS21} requires users to insert their PINs into their personal computers instead of inserting them into the dedicated hardware token; this approach is problematic as the PINs will be at a higher risk of being exposed to attackers because users' computers are (i) often connected to the internet, and (ii) used for various purposes, consequently, they are more likely to be broken into. Furthermore, the protocol relies on an additional trusted party as well, i.e., trusted users' computers. Specifically, for the protocol's security to hold, it is required that users' personal computers are fully trusted, in the case where the token or the server is corrupted, which is not desirable. In contrast, our protocol requires users to insert their PIN into the hardware token that is used only for authentication and is always disconnected from the internet. 
% 
% % 
% Furthermore, our protocol is secure in the standard model whereas the protocols in \cite{WangW18,JareckiJKSS21} are in the non-standard random oracle model. 

